The complex structure and peculiar internal motions of the planetary nebula NGC 6210

### 2020-03-03 ms.tex
Explicitly specify all subfolders for figures

\documentclass[useAMS, usenatbib]{mnras}
\pdfsuppresswarningpagegroup=1
%
\usepackage[spanish,es-minimal,english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\graphicspath{{tere-figs/}{figs/}}

@@

\begin{figure*}
\centering
  \includegraphics[width=0.7\textwidth]{Figure1.pdf}
  \caption{ }
\end{figure*}

\begin{figure*}
\centering
  \includegraphics[width=0.4\textwidth]{Figure2a.pdf}
  \caption{ }
\end{figure*}

\begin{figure*}
\centering
  \includegraphics[width=1\textwidth]{Figure3.pdf}
  \caption{ }
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.9\textwidth]{Figure8.png}
\includegraphics[width=0.42\textwidth]{N6210_ruso.pdf}
\quad
\includegraphics[width=0.427\textwidth]{opo9836f.jpg}
  \caption{}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.9\textwidth]{Figure6.pdf}
  \caption{  }
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.9\textwidth]{rendija-c-cont.pdf}
  \caption{  }
\end{figure*}

@@

\includegraphics[width=0.4\textwidth]{slit_t_ha_nii.pdf}
\includegraphics[width=0.4\textwidth]{slit_v_ha_nii.pdf}
\includegraphics[width=0.4\textwidth]{slit_w_ha_nii.pdf}
\includegraphics[width=0.2\textwidth]{slit_u_oiii.pdf}
\includegraphics[width=0.2\textwidth]{slit_s_oiii.pdf}
\includegraphics[width=0.2\textwidth]{slit_r_oiii.pdf}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{oiii-propermotions}
  \caption{Proper motions derived from two HST \oiii{} images (F502N
    filter) separated by 10.45 years, using the FLCT algorithm with a
    Gaussian window width of 10~pixels. The key at bottom left shows a
    proper motion of \SI{10}{mas.yr^{-1}}, corresponding to
    \SI{95}{km.s^{-1}} for an assumed distance of \SI{2}{kpc}.}
  \label{fig:proper-motions-oiii}
\end{figure}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{nii-propermotions}
  \caption{As Fig.~\ref{fig:proper-motions-oiii} but for two HST
    \nii{} images (F658N filter). Note that the field of view is
    cropped slightly smaller than for \oiii{}.}
  \label{fig:proper-motions-nii}
\end{figure}

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{turtle-peanut-map}
  \caption{
    Velocity features in the high-ionization shells,
    which have been identified in the \oiii{} slits.
    Left panel shows blue-shifted features,
    while right panel shows red-shifted features,
    each labelled with their line-of-sight velocity
    with respect to the nominal systemic velocity of \SI{40}{km.s^{-1}}.
    Solid lines show features in the inner shells,
    dashed lines show features in the intermediate shell,
    and dot-dashed lines show miscellaneous features between the two shells.
    The line width is a qualitative indicator of the brightness of each feature.
  }
  \label{fig:shell-velocity-components}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{turtle-shell-velocity-axes-annotated}
  \caption{
    Radial velocity versus position
    for the shell features shown in Fig.~\ref{fig:shell-velocity-components}.
    Results are shown along two axes:
    Axis~A (upper panel) is the apparent major projected axis of the inner shells,
    while Axis~B (lower panel) is perpendicular to this.
    Large blue circles show the inner shell,
    small red circles show the intermediate shell,
    and green triangles show miscellaneous features between the two shells.
    Darker colors indicate features that are closer to each respective axis.
    Colored lines are merely to guide the eye,
    and show possible interpretations of the shell kinematics along the two axes.
  }
  \label{fig:shell-velocity-axes}
\end{figure}

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{turtle-knot-complex-map}
  \caption{
    Velocity features in the low-ionization knot complexes,
    which have been identified in the \nii{} slits.
    Left panel shows blue-shifted features,
    while right panel shows red-shifted features,
    each labelled with their line-of-sight velocity
    with respect to the nominal systemic velocity of \SI{40}{km.s^{-1}}.
    The line width is a qualitative indicator of the brightness of each feature.
  }
  \label{fig:knot-complex-map}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{turtle-nii-knot-complexes}
  \caption{
    Reconstructed velocity channel maps from the \nii{} slit spectra,
    showing the red-shifted (left panel) and blue-shifted (right panel) knot complexes.
    Note that channel maps have not been spatially interpolated,
    so that the individual slit positions can be seen.
    Each color image is constructed from 3 channels, each of width \SI{20}{km.s^{-1}},
    as indicated on the figure.
    All velocities are with respect to the nominal heliocentric systemic velocity of \SI{-40}{km.s^{-1}}.
    The low-ionization emission components from Fig.~\ref{fig:knot-complex-map}
    have been classified into 5 knot complexes,
    which are shown as colored outlines. 
  }
  \label{fig:knot-complexes}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{turtle-knot-complexes-velocity-axes-annotated}
  \caption{
    Radial velocity versus position
    for the low-ionization features features shown in Fig.~\ref{fig:knot-complex-map}.
    Results are shown projected along along the same two axes,
    Axis~A (upper panel) and Axis~B (lower panel),
    as in Fig.~\ref{fig:shell-velocity-axes},
    but this time each feature is shown projected along both axes.
    The features are divided into different knot complexes,
    as shown in Fig.~\ref{fig:knot-complexes},
    which are indicated by symbol type and color.
    Symbol size is proportional to feature brightness (log scale)
    and symbol shade indicates position along the other axis (darker is more positive).
    Continuous lines show the same high ionization shells
    as in Fig.~\ref{fig:shell-velocity-axes}.
  }
  \label{fig:knot-complex-velocity-axes}
\end{figure}

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{turtle-lobes-simplified}
  \caption{
    Velocity components and systems in the outer lobes.
    (a)~Blue-shifted components identified in individual slits.
    (b)~Red-shifted components identified in individual slits.
    (c)~Classification of components into seven high-velocity systems (colored shapes)
    along three different axes (heavy dashed lines).
    (d)~Same but for eleven intermediate velocity systems.
  }
  \label{fig:outer-lobe-components}
\end{figure*}
\newcounter{Syscounter}
\newcommand\Sys[1]{%
  \setcounter{Syscounter}{#1}%
  \ensuremath{\mathrm{\Roman{Syscounter}}}%
}
\newcommand\SysP[1]{\ensuremath{\Sys{#1}^+}}
\newcommand\SysM[1]{\ensuremath{\Sys{#1}^-}}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{turtle-halo-map}
  \caption{
    Velocity components in the halo.
    Components are divided into three classes:
    inner halo (pink ellipses), outer halo (yellow ellipses),
    and halo knots (green ellipses).
  }
  \label{fig:halo-components}
\end{figure}

>>>>

\documentclass[useAMS, usenatbib]{mnras}
\pdfsuppresswarningpagegroup=1
%
\usepackage[spanish,es-minimal,english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}

@@

\begin{figure*}
\centering
  \includegraphics[width=0.7\textwidth]{tere-figs/Figure1}
  \caption{ }
\end{figure*}

\begin{figure*}
\centering
  \includegraphics[width=0.4\textwidth]{tere-figs/Figure2a}
  \caption{ }
\end{figure*}

\begin{figure*}
\centering
  \includegraphics[width=1\textwidth]{tere-figs/Figure3}
  \caption{ }
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.9\textwidth]{tere-figs/Figure8}
\includegraphics[width=0.42\textwidth]{tere-figs/N6210_ruso}
\quad
\includegraphics[width=0.427\textwidth]{tere-figs/opo9836f}
  \caption{}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.9\textwidth]{tere-figs/Figure6}
  \caption{  }
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.9\textwidth]{tere-figs/rendija-c-cont}
  \caption{  }
\end{figure*}

@@

\includegraphics[width=0.4\textwidth]{tere-figs/slit_t_ha_nii}
\includegraphics[width=0.4\textwidth]{tere-figs/slit_v_ha_nii}
\includegraphics[width=0.4\textwidth]{tere-figs/slit_w_ha_nii}
\includegraphics[width=0.2\textwidth]{tere-figs/slit_u_oiii}
\includegraphics[width=0.2\textwidth]{tere-figs/slit_s_oiii}
\includegraphics[width=0.2\textwidth]{tere-figs/slit_r_oiii}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/oiii-propermotions}
  \caption{Proper motions derived from two HST \oiii{} images (F502N
    filter) separated by 10.45 years, using the FLCT algorithm with a
    Gaussian window width of 10~pixels. The key at bottom left shows a
    proper motion of \SI{10}{mas.yr^{-1}}, corresponding to
    \SI{95}{km.s^{-1}} for an assumed distance of \SI{2}{kpc}.}
  \label{fig:proper-motions-oiii}
\end{figure}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/nii-propermotions}
  \caption{As Fig.~\ref{fig:proper-motions-oiii} but for two HST
    \nii{} images (F658N filter). Note that the field of view is
    cropped slightly smaller than for \oiii{}.}
  \label{fig:proper-motions-nii}
\end{figure}

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/turtle-peanut-map}
  \caption{
    Velocity features in the high-ionization shells,
    which have been identified in the \oiii{} slits.
    Left panel shows blue-shifted features,
    while right panel shows red-shifted features,
    each labelled with their line-of-sight velocity
    with respect to the nominal systemic velocity of \SI{40}{km.s^{-1}}.
    Solid lines show features in the inner shells,
    dashed lines show features in the intermediate shell,
    and dot-dashed lines show miscellaneous features between the two shells.
    The line width is a qualitative indicator of the brightness of each feature.
  }
  \label{fig:shell-velocity-components}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/turtle-shell-velocity-axes-annotated}
  \caption{
    Radial velocity versus position
    for the shell features shown in Fig.~\ref{fig:shell-velocity-components}.
    Results are shown along two axes:
    Axis~A (upper panel) is the apparent major projected axis of the inner shells,
    while Axis~B (lower panel) is perpendicular to this.
    Large blue circles show the inner shell,
    small red circles show the intermediate shell,
    and green triangles show miscellaneous features between the two shells.
    Darker colors indicate features that are closer to each respective axis.
    Colored lines are merely to guide the eye,
    and show possible interpretations of the shell kinematics along the two axes.
  }
  \label{fig:shell-velocity-axes}
\end{figure}

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/turtle-knot-complex-map}
  \caption{
    Velocity features in the low-ionization knot complexes,
    which have been identified in the \nii{} slits.
    Left panel shows blue-shifted features,
    while right panel shows red-shifted features,
    each labelled with their line-of-sight velocity
    with respect to the nominal systemic velocity of \SI{40}{km.s^{-1}}.
    The line width is a qualitative indicator of the brightness of each feature.
  }
  \label{fig:knot-complex-map}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/turtle-nii-knot-complexes}
  \caption{
    Reconstructed velocity channel maps from the \nii{} slit spectra,
    showing the red-shifted (left panel) and blue-shifted (right panel) knot complexes.
    Note that channel maps have not been spatially interpolated,
    so that the individual slit positions can be seen.
    Each color image is constructed from 3 channels, each of width \SI{20}{km.s^{-1}},
    as indicated on the figure.
    All velocities are with respect to the nominal heliocentric systemic velocity of \SI{-40}{km.s^{-1}}.
    The low-ionization emission components from Fig.~\ref{fig:knot-complex-map}
    have been classified into 5 knot complexes,
    which are shown as colored outlines. 
  }
  \label{fig:knot-complexes}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/turtle-knot-complexes-velocity-axes-annotated}
  \caption{
    Radial velocity versus position
    for the low-ionization features features shown in Fig.~\ref{fig:knot-complex-map}.
    Results are shown projected along along the same two axes,
    Axis~A (upper panel) and Axis~B (lower panel),
    as in Fig.~\ref{fig:shell-velocity-axes},
    but this time each feature is shown projected along both axes.
    The features are divided into different knot complexes,
    as shown in Fig.~\ref{fig:knot-complexes},
    which are indicated by symbol type and color.
    Symbol size is proportional to feature brightness (log scale)
    and symbol shade indicates position along the other axis (darker is more positive).
    Continuous lines show the same high ionization shells
    as in Fig.~\ref{fig:shell-velocity-axes}.
  }
  \label{fig:knot-complex-velocity-axes}
\end{figure}

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/turtle-lobes-simplified}
  \caption{
    Velocity components and systems in the outer lobes.
    (a)~Blue-shifted components identified in individual slits.
    (b)~Red-shifted components identified in individual slits.
    (c)~Classification of components into seven high-velocity systems (colored shapes)
    along three different axes (heavy dashed lines).
    (d)~Same but for eleven intermediate velocity systems.
  }
  \label{fig:outer-lobe-components}
\end{figure*}
\newcounter{Syscounter}
\newcommand\Sys[1]{%
  \setcounter{Syscounter}{#1}%
  \ensuremath{\mathrm{\Roman{Syscounter}}}%
}
\newcommand\SysP[1]{\ensuremath{\Sys{#1}^+}}
\newcommand\SysM[1]{\ensuremath{\Sys{#1}^-}}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/turtle-halo-map}
  \caption{
    Velocity components in the halo.
    Components are divided into three classes:
    inner halo (pink ellipses), outer halo (yellow ellipses),
    and halo knots (green ellipses).
  }
  \label{fig:halo-components}
\end{figure}
